Clustering exploration for `r params$sample_id`

### 2024-09-19 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

- `fetal_full_predicted.organ` is one of the 15 organs used for building the reference. 
We were nicely surprised that most of the cells from the Wilms tumor cohort maped to fetal kidney cells.

@@

- `fetal_full_predicted.annotation.l1` holds predicted cell type annotations that details further the four compartments, as for example:

>>>>

- `fetal_full_predicted.organ` is one of the 15 organs used for building the reference. 
We were nicely surprised that, for many of the samples, most of the cells from the Wilms tumor cohort mapped to fetal kidney cells.

@@

- `fetal_kidney_predicted.cell_type` holds predicted cell type annotations that details further the four compartments, as for example:
